Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-22 thesis/paper_draft.qmd
minor change, change params files for simulations

\vspace{2cm}

@@

@@

sim2_1 <- readRDS(paste0(path_lib, "S36-6-1_T50_M500.rds"))
sim2_2 <- readRDS(paste0(path_lib, "S36-6-1_T300_M500.rds"))

sim3_1 <- readRDS(paste0(path_lib, "S100-10-3-1_T50_M200_dense.rds"))
sim3_2 <- readRDS(paste0(path_lib, "S100-10-3-1_T300_M200_dense.rds"))

@@

p2_A <- plot_heatmap(sim2_1$A) +
  ggtitle("VAR(1) Coefficients Matrix") + theme_void()

p2_Sigma <- plot_heatmap(cov2cor(sim2_1$Sigma), T) +
  ggtitle("Correlation Matrix of Innovation process") + theme_void()

p2_A + p2_Sigma + plot_layout(ncol = 2) & theme(legend.position = "bottom")
```

@@

p3_A <- plot_heatmap(sim3_1$A) +
  ggtitle("VAR(1) Coefficients Matrix")

p3_Sigma <- plot_heatmap(cov2cor(sim3_1$Sigma), T) +
  ggtitle("Correlation Matrix of Innovation process")

p3_A + p3_Sigma + plot_layout(ncol = 1) & theme(legend.position = "right")
```

@@

sim_params_sparse <- readRDS(paste0(path, "/thesis/lib/params_S100_10_3_1_sparse46.rds"))
sim_params_sparse$Sigma |>
  cov2cor() |> 
  plot_heatmap(T)
```

>>>>

\vspace{1cm}

@@

\vspace{1cm}

***Keywords:** Coherent forecasts, Hierarchical time series, Covariance estimation, Australian tourism, Aggregation.*

@@

sim_params_S36 <- readRDS(paste0(path_lib, "params_S36_6_1.rds"))
sim_params_S100 <- readRDS(paste0(path_lib, "params_S100_10_3_1_dense.rds"))
sim_params_sparse <- readRDS(paste0(path_lib, "params_S100_10_3_1_sparse46.rds"))

@@

p36_A <- plot_heatmap(sim_params_S36$A) +
  ggtitle("VAR(1) Coefficients Matrix") + theme_void()

p36_Sigma <- plot_heatmap(cov2cor(sim_params_S36$Sigma), T) +
  ggtitle("Correlation Matrix of Innovation process") + theme_void()

p36_A + p36_Sigma + plot_layout(ncol = 2) & theme(legend.position = "bottom")
```

@@

p100_A <- plot_heatmap(sim_params_S100$A) +
  ggtitle("VAR(1) Coefficients Matrix")

p100_Sigma <- plot_heatmap(cov2cor(sim_params_S100$Sigma), T) +
  ggtitle("Correlation Matrix of Innovation process")

p100_A + p100_Sigma + plot_layout(ncol = 1) & theme(legend.position = "right")
```

@@

sim_params_sparse$Sigma |>
  cov2cor() |> 
  plot_heatmap(T)
```
